\documentclass[11pt,a4paper,sans]{moderncv}
% possible options include font size ('10pt', '11pt' and '12pt'), paper size
% ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and
% 'landscape') and font family ('sans' and 'roman')

\input{config}


\title{Curriculum Vitae}
%\extrainfo{additional information} 
%\quote{Some quote}                

% bibliography with mutiple entries
\usepackage{multibib}
\newcites{conferences}{{Papers in refereed conferences}}
\newcites{journals}{{Journals}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\AtBeginDocument{%
    \hypersetup{colorlinks,urlcolor=blue}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Commands
\newcommand\burl[1]{[\url{#1}]}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle%
% \today
\renewcommand{\listitemsymbol}{-~}            % change the symbol for lists
% \section{Personal Information}
% \cvlistitem{Age: 29}
% \cvlistitem{Date of birth: March 1st, 1990}
% \cvlistitem{Place of birth: Rosario, Santa Fe, Argentina}
% \cvlistitem{Nationalities: Argentinian, Italian}
% \cvlistitem{Argentinian Passport: 35130605N}
% \cvlistitem{Italian Passport: YA4033590}
% \cvlistitem{Marital Condition: Single}
\section{Education}
\cventry{2015--2023}{PhD Student in Computer Science}{National University of
  Rosario}{Rosario}{Santa Fe, Argentina}{}
\cvline{Thesis}{\emph{Effectful Improvement Theory}}
\cvline{Supervisor}{Dr. Mauro Jaskelioff}
% \cvline{description}{Cost relations to prove program optimizations in functional
% languages with algebraic effects.}
% \cvline{description}{Improvement Theory is theory based on a cost relation of programs where its basic
%   observation is related to improve certain resource consumption, such as
%   energy or evaluation steps. Since it is based on exact costs, it is extremely
%   useful to prove compilers optimization.
%   There is a fault that the theory depends on features of the evaluation of such
%   languages, therefore, if someone wants to use such theory for a new language,
%   she would have to derive a lot of theorems and lemmas before the theory
%   became useful.
%   This Thesis presents a way to derive Improvement Theories for different
%   languages given its interpreters have certain properties such as modularity and
%   monotonic cost consumption.}
% {I have a
% scholarship completely funded by \href{http://www.conicet.gov.ar/}{CONICET}, the national
% research council
% and I am currently working at
% \href{http://www.cifasis-conicet.gov.ar/}{CIFASIS}.}
\cventry{2008--2015}{Computer Science Degree}{National University
  of Rosario}{Rosario}{Santa Fe, Argentina}{
  Grade Point Average: 9.60. Top Student Award Class 2014--2015.}  % arguments 3
% \cvitem{}{Degree's Thesis}
\cvline{Thesis}{\emph{Simulation of Parallel Programs in Haskell}}
\cvline{Advisors}{Dr. Mauro Jaskelioff and Dr. Exequiel Rivas}
% \cvline{description}{%
%     The use of the basic parallel combinators in \emph{Haskell} produces a certain
% effect in run-time, which is the parallelization of our program. Since that
% effect is not directly observable, we can try and guess what happened using
% tools like \emph{ThreadScope}. However, one can not match the behavior of the
% program's execution and its source code. Therefore, in this work we designed an
% EDSL around the basic combinators to produce a \emph{parallel structure} of
% programs, a data type that reassembles how the parallel combinators were used in
% the source code, so one can see, and analyze the inherent parallel behavior of
% our programs. The aim of this work was the development of a tool to make
% parallelism observable, so one can use this information to help undergraduate
% students get a better understanding, or to study the parallelism of our
% programs.
% } 

\section{Experience}
\subsection{Postdoc Researcher}
\cventry{03/2023--Today}{Instituto Madrile\~no de Estudios
Avanzado}{Madrid}{Espa\~na}{}{%
Offline monitoring properties of smart-contracts.
Developing \emph{Termina}, a \textbf{non}-turing complete language designed to
write safe programs for satellites.
Theoretical research: developing a specification language breaking the barrier
between formal specifications and executable programs.
}{}
\subsection{Research Programmer}
\cventry{10/2022--02/2023}{Instituto Madrile\~no de Estudios
Avanzado}{Madrid}{Espa\~na}{}{%
Development of offline monitoring indexing providing a bridge between
HLola~\cite{HLola} and the Tezos Blockchain~(\url{https://tezos.com/}).
}{}
\subsection{Visiting PhD Student}
\cventry{09/2021-09/2022}{Instituto Madrile\~no de Estudios
Avanzado}{Madrid}{Espa\~na}{}{%
Mechanization of previous results in \emph{Coq} resulting in a new framework
called \emph{Multi} implemented to prove and study properties of multi-contract
interaction and different blockchain features\cite{Ceresa.2022.Multi}.
%
Collaboration on the development of online transaction
monitors~\cite{Capretto.2022.TransactionMonitors} and setchain~\cite{Capretto.2022.Setchain}.
}{}
\subsection{Intern}
\cventry{08/2020-02/2021}{Instituto Madrile\~no de Estudios
Avanzado}{Madrid}{Espa\~na}{}{%
Formalizing and implementing several blockchain execution strategies for
online and onchain smart contract monitoring.
%
We also explored:
\begin{itemize}
  \item solutions to offline monitoring blockchain and blockchain in order to
devise new high-level query language;
  %
  \item how to retrieve and analyze ephemeral data employed by the blockchain
ecosystem, e.g. the mempool, branch-blocks, for off-line monitoring implementations;
  %
  \item solutions to mitigate front-running attacks
\end{itemize}
}{}
\cventry{03/2013--09/2013}{Instituto Madrile\~no de Estudios
Avanzado}{Madrid}{Espa\~na}{}{%
Building a tool for synthesizing and automatic proving cryptographic
constructions for \href{www.easycrypt.info}{EasyCrypt}.
%
Consisted of: Learning about Modern Cryptography proofs, game simulation based
proofs.
Tactics implemented: field/ring equality, and automatic optimistic sampling
tactic.
Language employed: OCaml.
}{}

\subsection{Projects}
\cvline{Termina}{Transpiler from Termina language to C.}
\cvline{Multi}{Coq Multi Smart-Contract Interaction library exploring different
smart-contracts execution models.}
\cvline{HLola}{Haskell Lola
  implementation\burl{https://github.com/imdea-software/hlola}. Remote
  collaboration with the Stream Runtime Verification group at IMDEA-Software.} 
\cvline{QuickFuzz}{An automatic random fuzzer for common file formats. Open
Source project. Haskell Code:
\burl{https://github.com/CIFASIS/QuickFuzz}.}
\cvline{MegaDeTh}{An experimental automatic and \textbf{aggressive} instance
derivator in Haskell using Template Haskell. Open Source project. Haskell Code:
\burl{https://github.com/CIFASIS/megadeth}}

% \newpage

\subsection{Teaching}
\cventry{2019--2021}{Adjunct Professor}{National University of Rosario}{Rosario}{Argentina}{}
% \cventry{2019--}{Adjunct Professor}{Compilers}{National University of
%   Rosario}{}
\cvitem{Parallel and Concurrent Programs}{%
  I taught the basic mechanisms and problems of concurrent
  and parallel programming. It is taught in \emph{C} and \emph{Erlang}.}
\cvitem{Compilers Course}{This course is based on the implementation
of a full \emph{Tiger's} compiler, presented by Andrew Appel's book
\emph{Modern Compilers Implementation in ML}, without optimizations.}
\cventry{2011 - 2019}{Teacher Assistant}{National University of Rosario}{Rosario}{Argentina}{}
\cvitem{}{Worked in courses that involved:}
\cvlistitem{Data Structures and Algorithms in C}
\cvlistitem{Compiler Theory and Practice}
\cvlistitem{Concurrent Programming in Erlang}
\cvlistitem{Introduction to pure programming languages and Haskell}
\cvlistitem{Parallel Thinking in Haskell}
\cvlistitem{Introduction to Lambda Calculus, STLC, Intermediate functional programming in Haskell}
\cvlistitem{Introduction to Intuitionistic Logic}
\cvlistitem{Introduction to Generalized Abstract Data Types}
\cvitem{}{My responsibilities included: assisting and conducting practical exercising
  hours, proposing exams and final projects, and grading practice exams.}
\cventry{09/2015--02/2016}{Teacher}{Introduction to Mathematics}{National
University of Rosario}{}{Introductory course for pre-university students. I
presented an introduction to basic mathematics, as well as assist them in solving
exercises.}

\newpage
\subsection{Programming Competitions}
\cventry{2009}{3rd prize in the First Competitive Programming Encounter}{Santa Fe}{Argentina}{}{}{}
\cventry{2009}{Participant in South America Regional ACM-ICPC}{Buenos Aires}{Argentina}{}{}{}

\section{Skills}
\cvline{Languages}{Haskell (proficient), Agda (experienced), SML (prior experience), OCaml
  (prior experience), C (prior experience), Erlang (prior experience) }
\cvline{Proof Assistants}{Coq (experienced)}
\cvline{Specification Languages}{Z, CSP, TLA, Statecharts}
\cvline{Technologies}{ViM, Git, \LaTeX, Markdown, Org, GNU/Linux}
\cvline{Haskell Environment}{Property Based Testing (QuickCheck),
Metaprogramming (Template Haskell), XMonad, stack, cabal}
% \cvline{Others}{R, prolog, Scilab}

\subsection{Languages}
\cvitemwithcomment{Spanish}{Native}{}
\cvitemwithcomment{English}{Advance}{Fluent Written and Spoken}

% \section{Extra Courses}
\subsection{Courses}
\cventry{2019}{\(\pmb{\lambda}\)-Calculus and Reasonable Cost Models}{Buenos
Aires}{Argentina}{}{Introduction to reasonable cost models. Size
explosion. Abstract machines and a proof that the call-by-name weak \(\lambda\)-calculus is
reasonable. The call-by-value case. The open case and its different
presentation.The standardization theorem and the subterm property.}
\cventry{2018}{DeepSpec Summer School}{Princeton, NJ}{}{}{\burl{https://deepspec.org/event/dsss18/}}
\cventry{2018}{Topology II}{National University of Rosario}{Rosario}{Santa Fe,
    Argentina}{Introduction to algebraic Topology.}
\cventry{2018}{Topology I}{National University of Rosario}{Rosario}{Santa Fe,
    Argentina}{Introduction to Topology.}
\cventry{2018}{Haskell's Type System/GHC and its extensions}{Escuela de Verano
  de Ciencias Informáticas}{Rio Cuarto}{Cordoba,
  Argentina}{FlexibleContexts, FlexibleInstances, GADTs, Phantom Types,
RankNPoly, DataKinds, MultiParamTypeClasses, FunctionalDependencies,
TypeFamilies. \href{https://cs.famaf.unc.edu.ar/~hoffmann/rio18/}{Course Information}}
\cventry{2016}{Quantum Computing Introduction and Foundation of Programming
    Languages}{National University of Rosario}{Rosario}{Santa Fe,
    Argentina}{Introduction to quantum computing by Alejandro Díaz-Caro.}
\cventry{2016}{Programming with Categories}{National University of Rosario}{Rosario}{Santa Fe, Argentina}
{Introduction to Category Theory and Agda by Mauro Jaskelioff.}
\cventry{2014}{Interactive theorem proving: theory and practice}{University of
Buenos Aires}{Buenos Aires}{Buenos Aires, Argentina}{Introduction to Coq.
Natural deduction, Curry-Howard correspondence and Lambda Calculus.
\href{http://www.dc.uba.ar/events/eci/2014/cursos/ziliani}{Course Information}.}
\cventry{2011}{Type Theory}{National University of Rosario}{Rosario}{Santa Fe, Argentina}{Dependent Type Programming with Agda by Thorsten Altenkirch.}

\subsection{Online Courses}
\cventry{2015}{Paradox and Infinity}{Agustín
Rayo}{MIT}{Edx}{\href{https://verify.edx.org/cert/b343b0a81d54493289f2b06ca57c4fde}{Approved
Certification}.}

% Publications from a BibTeX file using the multibib package
\section{Publications}
%%%%%%%%%%%%%%%% Journals
\bibliographystylejournals{plain}
\nocitejournals{QF:Jorn}
\nocitejournals{CeresaEffectful}
\bibliographyjournals{journals}                   % 'publications' is the name of a BibTeX file
%%%%%%%%%%%%%%%% Conferences
\bibliographystyleconferences{plain}
\nociteconferences{HLola}
\nociteconferences{QF:Haskell}
\nociteconferences{Ceresa.2022.Multi}
\nociteconferences{Capretto.2022.Setchain}
\nociteconferences{Capretto.2022.TransactionMonitors}
\bibliographyconferences{conferences}                   % 'publications' is the name of a BibTeX file

% \subsection{Personal Skills}
% \cvitem{}{An active and continuous learner}
% \cvitem{}{Excellent predisposition to challenges}

% \clearpage
%-----       letter       ---------------------------------------------------------
% recipient data
%\recipient{}{Company, Inc.\\123 somestreet\\some city}
%\date{January 01, 1984}
%\opening{Dear Sir or Madam,}
%\closing{Yours faithfully,}
%\enclosure[Attached]{curriculum vit\ae{}}     % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%\makelettertitle

%\[ e=\lim_{n \to \infty} \left(1+\frac{1}{n}\right)^n \]
% \section{Research Statement}

% One of my main interest is functional programming languages.
% I think that we can use functional programming as a tool to
% understand how programming works, in particular pure functional languages give
% us the ways to explicitly observe what is going on, understand what we are
% observing, and build new concepts. It gives us the tools to think, create and
% test our ideas based in powerful mathematical concepts.

% I am working on a verified library in Agda to analyze costs models based on
% Category Theory. The main idea is to find a bridge between Improvement Theory
% developed by Andrew Sands and Functorial Semantics developed by Daniele Turi and
% Gordon Plotkin where I would like to build an improvement theory based on GSOS
% rules.

% My interest includes: functional programming, compiler theory, denotational
% semantics, generic programming, static analysis and type theory.
% I like Category Theory, abstract mathematical tools,
% and love Haskell.
%\makeletterclosing

\end{document}
%% end of file `template.tex'.

% \subsection{Have Experience With}
% \cvline{Formal Specification Languages}{Z, CSP, TLA/TLA+, Statecharts}
% \cvline{Database Theory}{SQL, Entity-Relationship Model, Relational Algebra}
% \cvline{Technologies}{Emacs}
% \cvline{Languages}{Erlang, OCaml}

%\section{Extra 2}
%\cvlistdoubleitem{Item 1}{Item 4}
%\cvlistdoubleitem{Item 2}{Item 5\cite{book1}}
%\cvlistdoubleitem{Item 3}{}
